%   Copyright (C) 2014  School of Information Sciences, Manipal



\newcommand{\projecttitle}{Boot-Time Optimization for Android on Intel Atom Architecture}
\newcommand{\projectauthors}{\normalsize Aurabindo J}
\newcommand{\institutename}{School of Information Sciences}
\newcommand{\university}{Manipal University, Manipal}
\newcommand{\rollno}{141021001}
\documentclass{mainreport}
%\linespread{1.5}
\usepackage{hyperref}
\usepackage{makeidx}
\usepackage{multirow}
\usepackage{nomencl}
\usepackage{pdfpages}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{listings}
\usepackage{color}
\usepackage{upquote}
\usepackage{relsize}
\usepackage{fancyvrb}
%\usepackage{biblatex}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}


\lstset{frame=tb,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}

%\usepackage{tocloft}


\newcommand{\tab}{\hspace*{2em}}
% for removing dots

\makeatletter
\renewcommand{\@dotsep}{10000} 
\makeatother

\renewcommand{\figurename}{Fig.}


\begin{document}

\maketitle
\makecertificate

\parindent 10mm
%\newgeometry{bottom=2.5cm,top=2.5cm}
\chapter*{Acknowledgment}\label{ack}\addcontentsline{toc}{chapter}{Acknowledgment}
{\label{ack} 

%\paragraph*{•}
\hspace{6mm} This project itself is an acknowledgment to the inspiration, drive and technical
assistance contributed by many individuals. I would like to express my heartfelt thanks to my project guides 
{\bf Dr. Harishchandra Hebbar} and {\bf Dr. Nandish Rao}
%\paragraph*{•}
I would like to thank all the teaching and non teaching faculties of {\bf School of Information Sciences}, 
in particular, for providing us with an ample environment and
infrastructure required to carry out this project. 

This project would not be possible without the support from {\bf Intel India}. I thank \
{\bf Mr. Satish A Hipparagi}, and {\bf Mr. Abhilash K.V.}, engineers at Intel,
for the inspiration and support rendered.

%\paragraph*{•}
I extend my heartfelt thanks to my parents, friends and well wishers for their 
support and timely help. Above all I thank the Almighty for His blessing and 
providing mercies at all stages of my work. \\[2cm]




\noindent Manipal \hfill Project Members

\noindent \today \hfill \institutename

 \hfill Manipal





}

\chapter*{Abstract}\label{Abstract}\addcontentsline{toc}{chapter}{Abstract}

{
\label{Abstract}



%\paragraph*{•}
\hspace{6mm} When Android framework was getting developed, systems using ARM core and
corresponding sub system architecture were widely used. As the ARM ecosystem evolved,
it established itself as one of the leading vehicle for Android platform. Consequently,
Android ecosystem also developed around ARM architecture including application
development, services and even system level optimization. When x86 core also entered
this Android ecosystem, effort was put in to make system level optimization for
Android products based on x86 Architecture.

This thesis aims at evaluating various known methods as well as finding new areas
for optimization. Optimization effort will be targeting at reducing the boot time of
the the system by evaluating various components which includes BIOS firmware,
Bootloader, Linux Kernel and other AOSP components.
%\end{center}
}

%generate table of contents
\tableofcontents

%\chapter*{List of Symbols}\label{symbol}\addcontentsline{toc}{chapter}{List of Symbols}
%\listofsymbols

%\input{symbol}

%\input{fig}

\listoffigures
\addcontentsline{toc}{chapter}{List of Figures}
%\listoftables
\addtocontents{lof}{\textbf{No.}\hspace{8 mm}\textbf{Figure}~\hfill\textbf{Page}\par}
%\newpage


\chapter*{List of Abbreviations}\label{abbrv}\addcontentsline{toc}{chapter}{List of Abbreviations}

\input{abbreviation}

%\chapter*{Report}\label{report}\addcontentsline{toc}{chapter}{Report}

\pagenumbering{arabic}

\input{introduction}
\input{boot}
\input{profiling}
\input{todo}
\input{conclusion}

%\chapter*{Datasheets}\label{datasheet}\addcontentsline{toc}{chapter}{Datasheets}

%{\label{nexys3}\includepdf[pages={-}]{Nexys3_rm.pdf} 
%{\label{nexys3}\includepdf[pages={1-1,8-10,11-14,18-20}]{Nexys3_rm.pdf} 
%{\label{nexys3}\includepdf[pages={1-1}]{spartan6.pdf} 

\nocite{*}
\bibliographystyle{plain}
\bibliography{master}

\end{document}
